Temperature Effects on Surface Sulfur Dioxide

### 2011-07-26 Background.tex
Filling in the images

@@

The various types of cyclic bonding arrangements are shown in Figure \ref{fig:cyclic-structures} for a \suldiox~molecule bonding to waters. Although three waters are shown in the molecular cartoon, any number of waters are allowed. Also, further bonding may occur to any of the participating molecules extraneous to the cyclic structure. Cycle types \Rmnum{2}, \Rmnum{3}, \Rmnum{4} in Figure \ref{fig:cyclic-structures} are cyclic structures in which the \suldiox~is a member of the cycle. Types \Rmnum{1} and \Rmnum{5} do not involve the \suldiox~in the bonding cycle, but are commonly encountered as the smallest cycle formed near the \suldiox. Type \Rmnum{3} is of particular interest because it is one of the most dominant \suldiox~bonding coordinations (``SO'', as shown later) configured as a cyclic structure.

@@

>>>>

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/double-cycle-type2-small.png}
		\caption{}
		\label{fig:cyclic-example}
	\end{center}
\end{figure}

@@

The various types of cyclic bonding arrangements are shown in Figure \ref{fig:cyclic-structures} for a \suldiox~molecule bonding to waters. Although three waters are shown in the molecular cartoon, any number of waters are allowed. Also, further bonding may occur to any of the participating molecules extraneous to the cyclic structure. Cycle types \Rmnum{1}, \Rmnum{2}, \Rmnum{3} in Figure \ref{fig:cyclic-structures} are cyclic structures in which the \suldiox~is a member of the cycle. Types \Rmnum{4} and \Rmnum{5} do not involve the \suldiox~in the bonding cycle, but are commonly encountered as the smallest cycle formed near the \suldiox. Type \Rmnum{3} is of particular interest because it is one of the most dominant \suldiox~bonding coordinations (``SO'', as shown later) configured as a cyclic structure.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycle-types-small.png}
		\caption{}
		\label{fig:cyclic-structures}
	\end{center}
\end{figure}

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/triple-cycle-types-small.png}
		\caption{}
		\label{fig:type-3-varieties}
	\end{center}
\end{figure}

### 2011-07-26 Introduction.tex
Filling in the images

The chemistry of our atmosphere is vastly complex and poorly understood. Reactions taking place on particle surfaces and liquid boundaries dominate many atmospheric chemical pathways, and guide terrestrial and industrial byproducts to their ultimate forms and destinations. How do atmospheric conditions affect the chemistry of environmental constituents?

>>>>

%The chemistry of our atmosphere is vastly complex and poorly understood. Reactions taking place on particle surfaces and liquid boundaries dominate many atmospheric chemical pathways, and guide terrestrial and industrial byproducts to their ultimate forms and destinations. How do atmospheric conditions affect the chemistry of environmental constituents?
